\documentclass{article} % For LaTeX2e
\usepackage{iclr2021_conference,times}
\usepackage[hyphens]{url}
\usepackage{graphicx}

% Optional math commands from https://github.com/goodfeli/dlbook_notation.
\input{math_commands.tex}

\usepackage{hyperref}
\usepackage{algorithm}
\usepackage{algorithmic}

\title{SPG-Bandit: Skill Profile Guided Bandit for Task Selection in LLM Agent Skill Evolution}

%\iclrfinalcopy

\author{Author Name \\
Affiliation \\
Address \\
\texttt{email} \\
}

\begin{document}

\maketitle

\begin{abstract}
Large language model agents can improve their performance through skill evolution---reflecting on execution trajectories and accumulating reusable knowledge. However, existing systems select practice tasks uniformly at random, ignoring the fact that different tasks contribute unequally to skill growth. We propose SPG-Bandit, a framework that casts task selection as a contextual bandit problem driven by a latent skill profile of the agent. SPG-Bandit uses Multidimensional Item Response Theory (MIRT) to estimate the agent's proficiency across multiple skill dimensions, then selects tasks using a gap-weighted upper confidence bound that prioritizes underdeveloped dimensions. Theoretically, we show that SPG-Bandit achieves $O(d_f \sqrt{T} \log T)$ cumulative regret by treating the gap-weighted reward as a convex combination of independent ridge regressions.
\end{abstract}

\section{Introduction}
\label{sec:introduction}

\subsection{Background and Motivation}

Large language model (LLM) agents have demonstrated the ability to perform complex tasks across a variety of environments, including embodied task completion, web navigation, and software engineering. A key capability enabling such generality is \emph{skill evolution}: the agent reflects on its execution trajectories, extracts reusable knowledge, and accumulates it in a growing skill library for future episodes.

Prior work has focused primarily on two aspects of this process. The first is \emph{skill quality}---how to extract more informative patterns from trajectories. For instance, SkillRL introduces a reflection mechanism that generates planning patterns from successful episodes and common mistakes from failures. The second is \emph{skill utilization}---how to organize, retrieve, and inject skills into the agent's prompt at inference time. These efforts include structured skill banks with category-specific retrieval, vector-database approaches, and dynamic prompting strategies.

A critical dimension has remained largely unexplored: \textbf{the order in which tasks are selected for practice.} Existing systems either cycle through a fixed task pool uniformly, sample tasks at random, or rely on hand-designed curricula that do not adapt to the agent's evolving competence. In RL, it is well-known that the task selection strategy can significantly affect learning efficiency. So, it is natural to ask: \emph{can we improve the efficiency and performance of skill evolution in LLM agents by adaptively selecting tasks based on the agent's current skill profile?}

\subsection{Contributions}

We present \textbf{SPG-Bandit} (Skill Profile Guided Bandit), a framework that casts task selection as a contextual bandit problem driven by a multidimensional skill profile of the agent.

Our core idea is to model the agent's latent proficiency across \(K\) skill dimensions using Multidimensional Item Response Theory (MIRT), then select tasks that maximize the expected progress toward underdeveloped dimensions.

Specifically, this proposal makes the following contributions:
\begin{enumerate}
    \item \textbf{Problem.} We identify and formalize the task selection problem in LLM agent skill evolution. We show that uniform and random selection---the default in existing systems---is suboptimal because different tasks contribute unequally to skill growth and the agent's skill profile is inherently multidimensional.
    \item \textbf{Method.} We propose SPG-Bandit, a framework that combines MIRT-based latent skill profiling with a gap-weighted bandit algorithm. The core idea is to maintain an online estimate of the agent's proficiency across \(K\) skill dimensions, then select tasks that maximize predicted progress toward underdeveloped dimensions.
    \item \textbf{Framework.} We provide a general framework which can easily combine with existing skill evolution methods. The framework is used to evaluate the effectiveness of SPG-Bandit in improving skill evolution efficiency and performance.
\end{enumerate}

\section{Problem Formulation}
\label{sec:problem}

\subsection{Notation and Setup}

Consider an LLM agent interacting with a fixed pool of tasks \(\mathcal{T} = \{1, 2, \dots, M\}\). At each discrete step \(t = 1, 2, \dots\), the agent selects a task \(\tau_t \in \mathcal{T}\), executes it, and receives a binary outcome \(y_t \in \{0, 1\}\) indicating task success or failure.

The agent possesses a \emph{latent skill profile} \(\mathbf{s}_t \in [0,1]^K\) representing its proficiency across \(K\) distinct skill dimensions. The profile is not directly observable; it must be inferred from observed outcomes. We denote the \emph{skill progress} between consecutive steps as \(\boldsymbol{\delta}_t = \mathbf{s}_{t+1} - \mathbf{s}_t\), which measures how much the agent's latent proficiency changes after executing task \(\tau_t\) and updating its skills via reflection.

Each task \(\tau\) is associated with a \emph{task embedding} \(\mathbf{e}_\tau \in \mathbb{R}^{d_c}\), typically derived from a sentence encoder applied to the task's natural-language goal description.

\subsection{Problem Definition}

We formalize adaptive task selection as a \emph{contextual bandit} problem. At each step \(t\):

\begin{enumerate}
    \item The agent observes its current context: the current skill profile \(\mathbf{s}_t\) and the embedding \(\mathbf{e}_\tau\) for each task \(\tau \in \mathcal{T}\).
    \item The agent selects an arm \(\tau_t \in \mathcal{T}\).
    \item The agent executes task \(\tau_t\), observes binary outcome \(y_t\), and updates its skills via reflection.
    \item The latent skill profile updates to \(\mathbf{s}_{t+1}\), and the realized progress \(\boldsymbol{\delta}_t = \mathbf{s}_{t+1} - \mathbf{s}_t\) is observed.
\end{enumerate}

To prioritize underdeveloped skill dimensions, we define a \emph{gap weight} vector:

\begin{equation}
    \mathbf{g}_t = \operatorname{softmax}\!\left( \frac{\mathbf{1} - \mathbf{s}_t}{\tau_g} \right),
    \label{eq:gap-def}
\end{equation}

where \(\tau_g > 0\) is a temperature parameter. The scalar reward at step \(t\) is the gap-weighted skill progress:

\begin{equation}
    r_t = \mathbf{g}_t^\top \boldsymbol{\delta}_t.
    \label{eq:reward}
\end{equation}

The goal is to maximize the expected cumulative reward:

\begin{equation}
    \max_{\pi} \; \mathbb{E}\left[ \sum_{t=1}^{H} r_t \;\middle|\; \tau_t \sim \pi(\cdot \mid \mathbf{s}_t, \{\mathbf{e}_\tau\}) \right],
    \label{eq:objective}
\end{equation}

where \(\pi\) denotes the task selection policy. Since the realized \(\boldsymbol{\delta}_t\) depends on the agent's internal reflection dynamics, we learn a surrogate prediction model \(\hat{\boldsymbol{\delta}}(\tau, \mathbf{s}_t)\) and use its gap-weighted form \(\mathbf{g}_t^\top \hat{\boldsymbol{\delta}}(\tau, \mathbf{s}_t)\) as the plug-in reward for bandit decision-making.


\section{Method}
\label{sec:method}

\subsection{Overview}

SPG-Bandit operates in two phases. In the \textbf{warmup phase}, the agent selects tasks uniformly to collect an initial set of interaction outcomes. After warmup, we run Multidimensional Item Response Theory (MIRT) to estimate the agent's latent skill profile for each warmup step, producing a sequence of skill deltas \(\{\boldsymbol{\delta}_t\}\) and item parameters for all tasks. We then train an MLP that predicts these deltas from task embeddings and the current profile.
    
In the \textbf{bandit phase}, at each step we compute a skill-progress gap vector \(\mathbf{g}_t\) from the current profile, use the Neural Linear UCB to predict each task's expected delta, and select the task with the highest gap-weighted UCB score. After execution, we update the profile via a Bayesian online MIRT and update the bandit's ridge regression parameters.

\subsection{Key Components}

\paragraph{Multidimensional IRT (MIRT).}
We model each task \(\tau\) with a \(K\)-dimensional discrimination vector \(\mathbf{a}_\tau \in \mathbb{R}^K\) and a difficulty scalar \(d_\tau \in \mathbb{R}\). Given the agent's current skill profile \(\mathbf{s} \in [0,1]^K\), the probability of success on task \(\tau\) is:

\begin{equation}
    p_\tau(\mathbf{s}) = \sigma\!\left( \mathbf{a}_\tau^\top \mathbf{s} - d_\tau \right),
    \label{eq:mirt}
\end{equation}

where \(\sigma(x) = 1/(1 + e^{-x})\). A high value in dimension \(k\) of \(\mathbf{a}_\tau\) means task \(\tau\) heavily depends on skill dimension \(k\); a high \(d_\tau\) means the task is generally difficult.

After collecting \(N\) warmup outcomes \(\{( \tau_t, y_t )\}_{t=1}^N\), we run an EM algorithm to jointly estimate:
\begin{itemize}
    \item The latent profiles \(\{\mathbf{s}_t\}_{t=1}^N\) .
    \item The item parameters \(\{(\mathbf{a}_\tau, d_\tau)\}_{\tau=1}^M\).
\end{itemize}

The E-step updates each \(\mathbf{s}_t\) via Newton-Raphson on the log-likelihood of observed outcomes for tasks selected up to step \(t\). The M-step optimizes each item's parameters via L-BFGS-B with \(\ell_2\) regularization.

After fitting, \textbf{sequential MIRT} is applied. For \(t = 1\), the profile before the step is initialized to zeros; for \(t \geq 2\), we run EM on the first \(t-1\) observations to obtain the profile before step \(t\), denoted \(\mathbf{s}_t^{\text{(bef)}}\). Running EM on the \(t\) observations gives the profile after step \(t\), denoted \(\mathbf{s}_t^{\text{(aft)}}\). The delta \(\boldsymbol{\delta}_t = \mathbf{s}_t^{\text{(aft)}} - \mathbf{s}_t^{\text{(bef)}}\) captures the progress attributable to executing task \(\tau_t\).

\paragraph{Delta prediction via MLP.}
To anticipate how much a candidate task will improve the agent, we train a two-layer MLP \(\Phi\) that maps the concatenation of the task embedding \(\mathbf{e}_\tau\) and current profile \(\mathbf{s}\) to a feature vector \(\boldsymbol{\phi} \in \mathbb{R}^{d_f}\):

\begin{align}
    \mathbf{h} &= \max(\mathbf{W}_1 [\mathbf{e}_\tau; \mathbf{s}] + \mathbf{b}_1, 0), \\
    \boldsymbol{\phi} &= \mathbf{W}_2 \mathbf{h} + \mathbf{b}_2.
\end{align}

A linear head \(\mathbf{W} \in \mathbb{R}^{d_f \times K}\) predicts the expected delta: \(\hat{\boldsymbol{\delta}} = \mathbf{W}^\top \boldsymbol{\phi}\). Training minimizes MSE over the warmup dataset \(\{([\mathbf{e}_{\tau_t}; \mathbf{s}_t^{\text{(bef)}}], \boldsymbol{\delta}_t)\}_{t=1}^N\).

\paragraph{Gap-weighted UCB selection.}
We treat delta prediction as a ridge regression problem. The covariance matrix \(\mathbf{A} = \lambda \mathbf{I} + \sum_{i=1}^t \boldsymbol{\phi}_i \boldsymbol{\phi}_i^\top\) captures uncertainty in the linear head estimate. At step \(t\), the estimate of the reward \(r_t = \mathbf{g}_t^\top \boldsymbol{\delta}\) for task \(\tau\) is \(\mathbf{g}_t^\top \hat{\boldsymbol{\delta}}_\tau\). To balance exploration, we add a UCB bonus scaled by \(\alpha > 0\):

\begin{equation}
    \text{score}(\tau) = \mathbf{g}_t^\top \mathbf{W}^\top \boldsymbol{\phi}_\tau + \alpha \sqrt{\boldsymbol{\phi}_\tau^\top \mathbf{A}^{-1} \boldsymbol{\phi}_\tau},
    \label{eq:score}
\end{equation}

where the first term is the gap-weighted exploitation (how much we expect this task to improve the weakest skill dimensions) and the second is a UCB exploration bonus scaled by \(\alpha > 0\). The task with the highest score is selected.

\paragraph{Online Bayesian MIRT update.}
After executing the selected task and observing outcome \(r\), we update the profile without re-running full EM. A single Newton-Raphson step on the log-posterior combines the IRT likelihood with a Gaussian prior centered at the previous profile:

\begin{equation}
    \mathbf{s}' = \mathbf{s} - \mathbf{H}^{-1} \nabla \mathcal{L}_{\text{post}},
\end{equation}

where \(\mathcal{L}_{\text{post}} = -\log p(r \mid \mathbf{s}, \mathbf{a}_\tau, d_\tau) + \frac{1}{2\sigma_s^2} \|\mathbf{s} - \mathbf{s}_0\|^2\). The resulting profile is clipped to \([0, 1]\).

\paragraph{Ridge regression update.}
After observing the realized delta \(\boldsymbol{\delta}\), we update the bandit's covariance and response:

\begin{align}
    \mathbf{A} &\mathrel{+}= \boldsymbol{\phi} \boldsymbol{\phi}^\top, \\
    \mathbf{B} &\mathrel{+}= \boldsymbol{\phi} \boldsymbol{\delta}^\top, \\
    \mathbf{W} &= \mathbf{A}^{-1} \mathbf{B}.
\end{align}

This ensures that the delta prediction adapts as more data is collected during the bandit phase.

\subsection{Algorithm}

Algorithm~\ref{alg:spg} summarizes the complete procedure.

\begin{algorithm}[t]
\caption{SPG-Bandit}
\label{alg:spg}
\begin{algorithmic}
\STATE {\bf Input:} Task pool \(\mathcal{T}\), warmup steps \(N\), bandit horizon \(H\), MLP feature dim \(d_f\), gap temperature \(\tau_g\), UCB exploration \(\alpha\), regularizer \(\lambda\), skill dimensions \(K\)
\STATE {\bf Phase 1: Warmup}
\FOR{\(t = 1\) to \(N\)}
    \STATE Select \(\tau_t \in \mathcal{T}\) uniformly
    \STATE Execute \(\tau_t\), observe \(y_t \in \{0,1\}\)
    \STATE Store \((\tau_t, y_t)\)
\ENDFOR
\STATE Run sequential MIRT EM on \(\{(\tau_t, y_t)\}\) \(\to\) profiles \(\{\mathbf{s}_t\}\), deltas \(\{\boldsymbol{\delta}_t\}\), item parameters \(\{\mathbf{a}_\tau, d_\tau\}\)
\STATE Train MLP \(\Phi\) on \(\{([\mathbf{e}_{\tau_t}; \mathbf{s}_t^{\text{(bef)}}], \boldsymbol{\delta}_t)\}\)
\STATE Initialize \(\mathbf{A} = \lambda \mathbf{I}_{d_f}\), \(\mathbf{B} = \mathbf{0}_{d_f \times K}\), current profile \(\mathbf{s} = \mathbf{s}_N\)
\STATE {\bf Phase 2: Bandit}
\FOR{\(t = 1\) to \(H\)}
    \STATE Compute gap \(\mathbf{g}_t = \operatorname{softmax}((\mathbf{1} - \mathbf{s}) / \tau_g)\)
    \FOR{each \(\tau \in \mathcal{T}\)}
        \STATE \(\boldsymbol{\phi}_\tau = \Phi([\mathbf{e}_\tau; \mathbf{s}])\), \(\hat{\boldsymbol{\delta}}_\tau = \mathbf{W}^\top \boldsymbol{\phi}_\tau\)
        \STATE \(\text{score}(\tau) = \mathbf{g}_t^\top \hat{\boldsymbol{\delta}}_\tau + \alpha \sqrt{\boldsymbol{\phi}_\tau^\top \mathbf{A}^{-1} \boldsymbol{\phi}_\tau}\)
    \ENDFOR
    \STATE \(\tau_t = \arg\max_\tau \text{score}(\tau)\)
    \STATE Execute \(\tau_t\), observe \(y_t\) and realized \(\boldsymbol{\delta}_t\)
    \STATE \(\mathbf{s} \gets \text{BayesUpdate}(\mathbf{s}, \mathbf{a}_{\tau_t}, d_{\tau_t}, y_t)\)
    \STATE \(\mathbf{A} \mathrel{+}= \boldsymbol{\phi}_{\tau_t} \boldsymbol{\phi}_{\tau_t}^\top\)
    \STATE \(\mathbf{B} \mathrel{+}= \boldsymbol{\phi}_{\tau_t} \boldsymbol{\delta}_t^\top\)
    \STATE \(\mathbf{W} = \mathbf{A}^{-1} \mathbf{B}\)
\ENDFOR
\end{algorithmic}
\end{algorithm}

\section{Theoretical Analysis}
\label{sec:theory}

We analyze the regret of SPG-Bandit under the assumption that the MLP feature extractor \(\Phi\) is fixed after warmup, and only the linear head \(\mathbf{W}\) is updated online. This matches the practical procedure described in Algorithm~\ref{alg:spg}. The reward at step \(t\) is \(r_t = \mathbf{g}_t^\top \boldsymbol{\delta}_t\), and the bandit selects the task maximizing \(\mathbf{g}_t^\top \mathbf{W}_{t-1}^\top \boldsymbol{\phi}_\tau + \alpha \sqrt{\boldsymbol{\phi}_\tau^\top \mathbf{A}_{t-1}^{-1} \boldsymbol{\phi}_\tau}\).

\subsection{Assumptions}

\begin{enumerate}
    \item \textbf{(Linear realizability.)} For each skill dimension \(k \in \{1,\dots,K\}\), there exists a true weight vector \(\mathbf{w}_k^* \in \mathbb{R}^{d_f}\) such that \(\mathbb{E}[\delta_t[k] \mid \boldsymbol{\phi}_{\tau_t}] = \mathbf{w}_k^{*\top} \boldsymbol{\phi}_{\tau_t}\). Collecting all dimensions, \(\mathbb{E}[\boldsymbol{\delta}_t \mid \boldsymbol{\phi}_{\tau_t}] = \mathbf{W}^{*\top} \boldsymbol{\phi}_{\tau_t}\) with \(\mathbf{W}^* = [\mathbf{w}_1^*, \dots, \mathbf{w}_K^*]\).
    \item \textbf{(Bounded features.)} \(\|\boldsymbol{\phi}_\tau\|_2 \leq 1\) for all \(\tau \in \mathcal{T}\).
    \item \textbf{(Sub-Gaussian noise.)} The per-dimension noise \(\eta_{t,k} = \delta_t[k] - \mathbf{w}_k^{*\top} \boldsymbol{\phi}_{\tau_t}\) is \(\sigma\)-sub-Gaussian.
\end{enumerate}

Assumption~1 is the standard linear realizability condition in contextual bandit theory. The feature vector \(\boldsymbol{\phi}_\tau\) is produced by a frozen MLP trained during warmup, so the linear head operates on a fixed representation.

\subsection{Regret Bound}

Define the instantaneous regret at step \(t\) as the gap between the reward of the optimal task and the chosen task:

\begin{equation}
    r_t^* - r_t = \mathbf{g}_t^\top \mathbf{W}^{*\top} \boldsymbol{\phi}_{\tau_t^*} - \mathbf{g}_t^\top \mathbf{W}^{*\top} \boldsymbol{\phi}_{\tau_t},
    \label{eq:regret-def}
\end{equation}

where \(\tau_t^* = \arg\max_\tau \mathbf{g}_t^\top \mathbf{W}^{*\top} \boldsymbol{\phi}_\tau\) is the optimal choice under the true weights.

We first establish that the score function is a valid upper confidence bound.

\paragraph{Lemma 1 (Per-dimension confidence ellipsoid).}
Let \(\mathbf{A}_t = \lambda \mathbf{I} + \sum_{i=1}^t \boldsymbol{\phi}_i \boldsymbol{\phi}_i^\top\). Under Assumptions~1--3, with probability at least \(1 - \delta/K\), for any dimension \(k\):

\begin{equation}
    |\boldsymbol{\phi}^\top \hat{\mathbf{w}}_{t,k} - \boldsymbol{\phi}^\top \mathbf{w}_k^*| \leq \beta_t \sqrt{\boldsymbol{\phi}^\top \mathbf{A}_t^{-1} \boldsymbol{\phi}},
    \label{eq:dim-ucb}
\end{equation}

where \(\beta_t = \sigma \sqrt{2 \log(K/\delta) + d_f \log(1 + t / (d_f \lambda))} + \sqrt{\lambda} S\), with \(S\) an upper bound on \(\|\mathbf{w}_k^*\|_2\).


\paragraph{Lemma 2 (Gap-weighted UCB).}
Let \(\mathbf{g}_t\) be any probability vector (i.e., \(\mathbf{g}_t[k] \geq 0\) and \(\sum_{k=1}^K \mathbf{g}_t[k] = 1\)). With probability at least \(1 - \delta\):

\begin{equation}
    \left| \mathbf{g}_t^\top \hat{\boldsymbol{\delta}}_\tau - \mathbf{g}_t^\top \mathbf{W}^{*\top} \boldsymbol{\phi}_\tau \right| \leq \beta_t \sqrt{\boldsymbol{\phi}_\tau^\top \mathbf{A}_{t-1}^{-1} \boldsymbol{\phi}_\tau},
    \label{eq:gap-ucb}
\end{equation}

where \(\hat{\boldsymbol{\delta}}_\tau = \mathbf{W}_{t-1}^\top \boldsymbol{\phi}_\tau\).

\paragraph{Proof.}
Unpacking the left side:
\[
\mathbf{g}_t^\top \hat{\boldsymbol{\delta}}_\tau - \mathbf{g}_t^\top \mathbf{W}^{*\top} \boldsymbol{\phi}_\tau
= \sum_{k=1}^K \mathbf{g}_t[k] \left( \boldsymbol{\phi}_\tau^\top \hat{\mathbf{w}}_{t-1,k} - \boldsymbol{\phi}_\tau^\top \mathbf{w}_k^* \right).
\]
Applying Lemma~1 to each term and using \(\mathbf{g}_t[k] \geq 0\):
\[
\left| \sum_{k=1}^K \mathbf{g}_t[k] \left( \boldsymbol{\phi}_\tau^\top \hat{\mathbf{w}}_{t-1,k} - \boldsymbol{\phi}_\tau^\top \mathbf{w}_k^* \right) \right|
\leq \sum_{k=1}^K \mathbf{g}_t[k] \cdot \beta_t \sqrt{\boldsymbol{\phi}_\tau^\top \mathbf{A}_{t-1}^{-1} \boldsymbol{\phi}_\tau}
= \beta_t \sqrt{\boldsymbol{\phi}_\tau^\top \mathbf{A}_{t-1}^{-1} \boldsymbol{\phi}_\tau},
\]
where the last equality uses \(\sum_k \mathbf{g}_t[k] = 1\). This confirms that \(\text{score}(\tau) = \mathbf{g}_t^\top \mathbf{W}_{t-1}^\top \boldsymbol{\phi}_\tau + \alpha \sqrt{\boldsymbol{\phi}_\tau^\top \mathbf{A}_{t-1}^{-1} \boldsymbol{\phi}_\tau}\) is a valid upper confidence bound when \(\alpha \geq \beta_t\).

\paragraph{Lemma 3 (Instantaneous regret).}
With probability at least \(1 - \delta\), the instantaneous regret at step \(t\) satisfies:

\begin{equation}
    r_t^* - r_t \leq 2\beta_t \sqrt{\boldsymbol{\phi}_{\tau_t}^\top \mathbf{A}_{t-1}^{-1} \boldsymbol{\phi}_{\tau_t}}.
    \label{eq:inst-regret}
\end{equation}

\paragraph{Proof.}
From Lemma~2, the score upper-bounds the true reward: \(\text{score}(\tau) \geq \mathbf{g}_t^\top \mathbf{W}^{*\top} \boldsymbol{\phi}_\tau\) for all \(\tau\). Therefore \(\mathbf{g}_t^\top \mathbf{W}^{*\top} \boldsymbol{\phi}_{\tau_t^*} \leq \text{score}(\tau_t^*) \leq \text{score}(\tau_t)\). Using the lower bound from Lemma~2 on the chosen arm:

\[
r_t^* - r_t = \mathbf{g}_t^\top \mathbf{W}^{*\top} \boldsymbol{\phi}_{\tau_t^*} - \mathbf{g}_t^\top \mathbf{W}^{*\top} \boldsymbol{\phi}_{\tau_t}
\leq \text{score}(\tau_t) - \left( \mathbf{g}_t^\top \hat{\boldsymbol{\delta}}_{\tau_t} - \beta_t \sqrt{\boldsymbol{\phi}_{\tau_t}^\top \mathbf{A}_{t-1}^{-1} \boldsymbol{\phi}_{\tau_t}} \right)
= 2\beta_t \sqrt{\boldsymbol{\phi}_{\tau_t}^\top \mathbf{A}_{t-1}^{-1} \boldsymbol{\phi}_{\tau_t}}.
\]

\paragraph{Theorem 1 (Cumulative regret).}
Under Assumptions~1--3 and setting \(\alpha = \beta_T\), the cumulative regret over \(T\) steps satisfies with probability at least \(1 - \delta\):

\begin{equation}
    R_T = \sum_{t=1}^T (r_t^* - r_t) = O\left( d_f \sqrt{T} \log T \right).
    \label{eq:cum-regret}
\end{equation}

\paragraph{Proof sketch.}
Summing Lemma~3 over \(t = 1,\dots,T\):

\[
R_T \leq 2\beta_T \sum_{t=1}^T \sqrt{\boldsymbol{\phi}_{\tau_t}^\top \mathbf{A}_{t-1}^{-1} \boldsymbol{\phi}_{\tau_t}}
\leq 2\beta_T \sqrt{ T \sum_{t=1}^T \boldsymbol{\phi}_{\tau_t}^\top \mathbf{A}_{t-1}^{-1} \boldsymbol{\phi}_{\tau_t} },
\]

where the second inequality is Cauchy-Schwarz. By the standard ellipsoid potential lemma, \(\sum_{t=1}^T \|\boldsymbol{\phi}_t\|_{\mathbf{A}_{t-1}^{-1}}^2 \leq 2 d_f \log(1 + T / (d_f \lambda))\). Substituting and expanding \(\beta_T\):

\[
R_T \leq 2\beta_T \sqrt{ 2 T d_f \log\!\left(1 + \frac{T}{d_f \lambda}\right) } = O\!\left( d_f \sqrt{T} \log T \right).
\]

This matches the standard LinUCB regret rate up to a factor of \(d_f\), confirming that SPG-Bandit achieves sub-linear regret despite the multi-dimensional skill structure. The key insight is that the gap weight vector \(\mathbf{g}_t\) acts as a convex combination over the \(K\) independent ridge regressions, preserving the confidence bound property without incurring an additional \(O(K)\) penalty.





% \bibliography{refs}
% \bibliographystyle{iclr2021_conference}

% \appendix
% \section{Appendix}

\end{document}
